---
title: "Mapping scheme indicators to Constituencies"
subtitle: "Merging databases on GP name"
output: 
  html_document:
    css: "css/style.css"
    df_print: default
    number_sections: no
    self_contained: no
    toc: no
    toc_float:
      collapsed: no
---

<br /> Last updated: `r format(Sys.time(), '%d %B, %Y')` (See [changelog](https://github.com/cbgaindia/obi-constituency-data-mapping/commits/main)).



### Results {.tabset}

<br />

#### Scheme-Wise

```{r chunk-options, include=FALSE}
# Options for building this document
knitr::opts_chunk$set(
  fig.height=5, 
  fig.width=10, 
  fig.align='center',
  echo=FALSE,
  message=FALSE,
  warning=FALSE
)
```

```{r function-to-summarise-mapping-for-scheme}
source("../scripts/libraries.R")
scheme_to_summarise <- c("mnrega-2018-19","mnrega-2019-20","pmagy-2018-19","pmagy-2019-20")

summarise_scheme_mapping <- function(scheme_to_summarise){
  
  # Read files
  scheme_mapping_summary <-
    readr::read_csv(glue(
      "../data/results/{scheme_to_summarise}-geography-mapping-summary.csv"
    ))

  # Evaluate percentage mapping for each geographic entity  
  total_districts <-
    scheme_mapping_summary %>% select(g_district) %>% unique() %>% nrow()
  total_blocks <-
    scheme_mapping_summary %>% select(g_district, g_block) %>% unique() %>% nrow()
  total_gps <-
    scheme_mapping_summary %>% select(g_district, g_block, g_gp) %>% unique() %>% nrow
  
  total_districts_mapped <-
    scheme_mapping_summary %>% select(g_district, district_mapped) %>% unique %>% filter(district_mapped ==
                                                                                           "yes") %>% nrow()
  total_blocks_mapped <-
    scheme_mapping_summary %>% select(g_district, g_block, block_mapped) %>% unique() %>% filter(block_mapped ==
                                                                                                   "yes") %>% nrow()
  total_gps_mapped <-
    scheme_mapping_summary %>% select(g_district, g_block, g_gp, gp_mapped) %>% unique() %>% filter(gp_mapped ==
                                                                                                      "yes") %>% nrow()
  
  # bind rows in a dataframe

  mapping_summary_table <- data.frame()
  variables_to_include <- c("districts","blocks","gps")
  for(i in 1:length(variables_to_include)){
    var_type <- variables_to_include[[i]] %>% stringr::str_to_title()
    var_total <-
      ifelse(
        var_type == "Districts",
        total_districts,
        ifelse(var_type == "Blocks", total_blocks, total_gps)
      )
    var_mapped <-
      ifelse(
        var_type == "Districts",
        total_districts_mapped,
        ifelse(var_type == "Blocks", total_blocks_mapped, total_gps_mapped)
      )
    var_df <-
      data.frame('Type' = var_type,
                 'Total' = var_total,
                 'Mapped' = var_mapped)
    var_df$MappingPercent <- var_df$Mapped / var_df$Total*100
    var_df$scheme <- ifelse(scheme_to_summarise == "mnrega-2018-19","MNREGA (2018-19)",ifelse(scheme_to_summarise == "mnrega-2019-20","MNREGA (2019-20)",ifelse(scheme_to_summarise == "pmagy-2018-19","PMAGY (2018-19)","PMAGY (2019-20)")))
    mapping_summary_table <- bind_rows(mapping_summary_table ,var_df)
  }
  
  return(mapping_summary_table)
} 
```

```{r generate-summary-for-each-scheme}

all_schemes_mapping_summary <- lapply(scheme_to_summarise, summarise_scheme_mapping)
all_schemes_mapping_summary <- bind_rows(all_schemes_mapping_summary)

```

```{r display-results}
bullet_green <- "<span style=\"color:green\">&#8226;</span>"
bullet_red <- "<span style=\"color:red\">&#8226;</span>"

all_schemes_mapping_summary_t <-
  all_schemes_mapping_summary %>% gt(rowname_col = "Type", groupname_col = "scheme") %>% tab_header(title = "Scheme Geography Mapping Summary") %>% fmt_number(
    columns = c("Total", "Mapped"),
    use_seps = TRUE,
    decimals = 0
  ) %>% fmt_percent(columns = "MappingPercent",
                    scale_values = FALSE,
                    decimals = 2) %>% text_transform(
  locations = cells_body(columns = Mapped,
                         rows = Total == Mapped),
  fn = function(x)
    paste(x, bullet_green)
) %>% text_transform(
  locations = cells_body(columns = Mapped,
                         rows = Mapped < Total),
  fn = function(x)
    paste(x, bullet_red)
) %>%  tab_options(table.width = pct(80),table.align = "center",
                   heading.background.color = "#F7EFB2",
                 row_group.font.weight = "bold",
                    column_labels.font.size = "small",
                     table.border.top.color =  "#000",
                 table.border.top.width = 2,
                 table_body.border.bottom.color =  "#000",
                 table_body.border.bottom.width = 2,
    table.font.size = "small",
    row_group.font.size = "small",
    data_row.padding = px(3),
      row_group.background.color = "#e8e8e4", row_group.border.bottom.color = "#8d99ae") %>%  tab_style(
    style = cell_text(weight = "bold", font = google_font(name = "Roboto")),
    locations = cells_body(columns = MappingPercent)
  )


all_schemes_mapping_summary_t
```

#### District Wise {.tabset}

```{r district-level-summary}

district_mapping_summary <- function(scheme_to_summarise){
    # Read files
  scheme_mapping_summary <-
    readr::read_csv(glue(
      "../data/results/{scheme_to_summarise}-geography-mapping-summary.csv"
    ))
  
  
   district_total <- scheme_mapping_summary %>% group_by(g_district) %>% summarise(total_GP = length(g_match_id), mapped_GP=length(g_match_id[gp_mapped=="yes"])) %>% mutate(mapping_percent=round(mapped_GP/total_GP*100))
   
   district_total$scheme_name <- scheme_to_summarise
  
   return(district_total)
}

district_wise_mapping_summary <- lapply(scheme_to_summarise, district_mapping_summary)

```


```{r generate-district-summary-function}

district_wise_mapping_summary <- bind_rows(district_wise_mapping_summary)

generate_district_wise_tables <- function(scheme_name){
  district_wise_mapping_summary_scheme <- district_wise_mapping_summary[district_wise_mapping_summary$scheme_name==scheme_name,]
district_wise_mapping_summary_scheme$scheme_name <- NULL
  district_wise_mapping_summary_t <- district_wise_mapping_summary_scheme %>% arrange(desc(mapping_percent)) %>% gt(rowname_col = "g_district") %>%    tab_stubhead(label = "District") %>%  cols_label(
    g_district = "District",
    total_GP = "totalGP",
    mapped_GP = "mappedGP",
    mapping_percent = "MappingPercent"
  ) %>% fmt_number(
    columns = c("total_GP", "mapped_GP"),
    use_seps = TRUE,
    decimals = 0
  ) %>% fmt_percent(columns = "mapping_percent",
                    scale_values = FALSE,
                    decimals = 0) %>% text_transform(
  locations = cells_body(columns = mapping_percent,
                         rows = total_GP == mapped_GP),
  fn = function(x)
    paste(x, bullet_green)
) %>% text_transform(
  locations = cells_body(columns = mapping_percent,
                         rows = mapped_GP < total_GP),
  fn = function(x)
    paste(x, bullet_red)
) %>%  tab_options(table.width = pct(80),table.align = "center",
                    column_labels.font.size = "small",
                     table.border.top.color =  "#000",
                 table.border.top.width = 2,
                 table_body.border.bottom.color =  "#000",
                 table_body.border.bottom.width = 2,
    table.font.size = "small",
    row_group.font.size = "small",
    data_row.padding = px(3)) %>%  tab_style(
    style = cell_text(weight = "bold", font = google_font(name = "Roboto")),
    locations = cells_body(columns = mapping_percent)
  )
  
  return(district_wise_mapping_summary_t)
}

```

##### MNREGA (2018-19)
```{r mnrega-2018-district-summary}
generate_district_wise_tables(scheme_name = scheme_to_summarise[[1]])


```


##### MNREGA (2019-20)
```{r mnrega-2019-district-summary}
generate_district_wise_tables(scheme_name = scheme_to_summarise[[2]])


```

##### PMAGY (2018-19)
```{r pmagy-2018-district-summary}
generate_district_wise_tables(scheme_name = scheme_to_summarise[[3]])

```

##### PMAGY (2019-20)
```{r pmagy-2019-district-summary}
generate_district_wise_tables(scheme_name = scheme_to_summarise[[4]])

```

---

<br />



### Dataset Links

| Scheme | Year    | Geographic Mapping Summary | Updated Scheme Data File  |
|:------:| :-----: | :--------------:| :----------------: |
| MNREGA | 2018-19 | [Link](../data/results/mnrega-2018-19-geography-mapping-summary.csv)        |   [Link](../data/scheme/MNREGA/odisha/2018-19/updated/odisha-mnrega-2018-updated.csv)           |
MNREGA | 2019-20 | [Link](../data/results/mnrega-2019-20-geography-mapping-summary.csv)| [Link](..//data/scheme/MNREGA/odisha/2019-20/updated/odisha-mnrega-2019-updated.csv)           |
PMAGY  | 2018-19 | [Link](../data/results/pmagy-2018-19-geography-mapping-summary.csv)        | [Link](../data/scheme/PMAGY/odisha/2018-19/updated/odisha-pmagy-2018-updated.csv)           |
PMAGY  | 2019-20 | [Link](../data/results/pmagy-2019-20-geography-mapping-summary.csv) | [Link](../data/scheme/PMAGY/odisha/2019-20/updated/odisha-pmagy-2019-updated.csv)           |


#### Files shared by CBGA

- **Geography File** for Odisha -- [Link](../data/geography/updated/geo-odisha-updated.csv)

- **Data for scheme indicators**
  - MNREGA 2018-19 - [Link](../data/scheme/MNREGA/odisha/2018-19/raw/csv/MGNREGA_Odisha_2018-19_040621.csv)
  - MNREGA 2019-20 - [Link](../data/scheme/MNREGA/odisha/2019-20/raw/csv/MGNREGA-Odisha-2019-20_040621.csv)
  - PMAGY 2018-19 - [Link](../data/scheme/PMAGY/odisha/2018-19/raw/csv/PMAYG-Odisha 2018-19_040621.csv)
  - PMAGY 2019-20 - [Link](../data/scheme/PMAGY/odisha/2019-20/raw/csv/PMAYG-Odisha 2019-20_040621.csv)

<br />

#### Dataset Descriptions

1. **Geographic Mapping Summary** -- To check which entities (district/block/village) from the Geography file were mapped to entities in the scheme file. 
2. **Updated Scheme Data File** -- Scheme indicators with updated geographies as per the geography file.
3. The **Geography File** contains the list of all Gram Panchayats located within an assembly and parliamentary constituency. 


---



